Climate Change Health Impact Assessments: Farmer Suicide and Drought Case Study.

### 2013-10-04 presentations-india-mssrf/presentation-mssrf.tex
half done

% Created 2013-06-26 Wed 11:16
\documentclass[bigger]{beamer}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\mode<beamer>{\usetheme{Madrid}}
\usepackage{verbatim}
\usepackage{color}
\usepackage{amsmath,amsfonts,amssymb}
\providecommand{\alert}[1]{\textbf{#1}}

\title{Open Software - Restricted Data:  A Suicide/Climate Case Study.}
\author{Ivan Hanigan$^1$, David Fisher$^2$, Steven McEachern$^3$}
\date{June 26, 2013}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs Org-mode version 7.9.3f}}

@@

\begin{itemize}
\item Restrictions on data access have increased recently
\item Concerns regarding reproducibility of data analyses
\item Access to data and analytic software addresses the:\\
 \textbf{Replicability Crisis}, (Peng 2011, \emph{Science}, 334;6060)
\item We built a safe Sever/Client IT environment for this
\item We show a Case Study of Suicide and Climate Impacts research
\end{itemize}
\end{frame}
\section{Methods}
\label{sec-2}
\begin{frame}
\frametitle{Methods}
\label{sec-2-1}

\begin{figure}[!h]
\centering
\includegraphics[width=.65\textwidth]{opensoft.pdf}
\caption{1. System Design}
\label{fig:sys}
\end{figure}
\end{frame}
\section{Results}
\label{sec-3}
\begin{frame}
\frametitle{Results (Hanigan et al, 2012, \emph{PNAS}, 109;35)}
\label{sec-3-1}

\begin{footnotesize}
\begin{itemize}
\item {\color{red}Restricted Health and Climate data} and 
\item {\color{blue}Less Restricted Population data} 
\end{itemize}
(Colours refer to data storage and access rules shown in Figure 1).
\begin{eqnarray*}
        log({\color{red} O_{ijk}})  & = & s({\color{red}ExposureVariable})  + {\color{blue} OtherExplanators}  \\
        & &   + AgeGroup_{i} + Sex_{j} \\
        & &   + {\color{blue} SpatialZone_{k}}  \\
        & &  + sin(Time \times 2 \times \pi) + cos(Time \times 2 \times \pi) \\
        & &  + Trend \\
        & &   + offset({\color{blue} log(Pop_{ijk})})\\
\end{eqnarray*}
\end{footnotesize}
\begin{tiny}
\noindent Where:\\
        \indent ${\color{red}O_{ijk}}$ = Outcome (counts) by Age$_{i}$, Sex$_{j}$ and SpatialZone$_{k}$ \\
        \indent {\color{red}ExposureVariable} = Data with {\color{red}Restrictive Intellectual Property~(IP)} \\
        \indent {\color{blue}OtherExplanators} = Other {\color{blue}Less Restricted}  Explanatory variables \\
        \indent s( ) = penalized regression splines \\
        \indent ${\color{blue} SpatialZone_{k}}$  = {\color{blue} Less Restricted} data representing the $SpatialZone_{k}$  \\
        \indent Trend = Longterm smooth trend(s) \\
        \indent ${\color{blue}Pop_{ijk}}$ = interpolated Census populations, by time in each group\\
\end{tiny}
\end{frame}
\begin{frame}
\frametitle{Future (Bambrick et al, 2008, Garnaut Review)}
\label{sec-3-2}

@@

\end{footnotesize}
\end{frame}
\section{Conclusion}
\label{sec-4}
\begin{frame}
\frametitle{Conclusion}
\label{sec-4-1}

This system:
\begin{itemize}
\item Enables data analysis in a safe environment
\item Allows comparison of multiple climate scenarios and assumptions
\item Demonstrated with a Climate/Health Impact Assessment
\end{itemize}
\begin{itemize}
\begin{large}
\item And this is Reproducible
\end{large}
\end{itemize}
\end{frame}
\section{Acknowledgements}
\label{sec-5}
\begin{frame}
\frametitle{Acknowledgements}
\label{sec-5-1}

\includegraphics[width=4cm]{ANU_LOGO_cmyk_56mm.png}
\includegraphics[width=3cm]{andslogo.pdf}
\includegraphics[width=3cm]{deptlogo.pdf} \\
\begin{footnotesize}
This project is supported by the Australian National Data Service through the National Collaborative Research Infrastructure Strategy Program and the Education Investment Fund (EIF) Super Science Initiative.

More information from:
\begin{itemize}
\item \texttt{ivan.hanigan@gmail.com}
\item \texttt{http://opensoftware-restricteddata.github.io}
\end{itemize}
\end{footnotesize}
\end{frame}
\section{References}
\label{sec-6}
\begin{frame}
\frametitle{References}
\label{sec-6-1}

>>>>

% Created 2013-10-04 Fri 18:48
\documentclass[bigger]{beamer}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\mode<beamer>{\usetheme{Madrid}}
\usepackage{verbatim}
\usepackage{color}
\usepackage{amsmath,amsfonts,amssymb}
\providecommand{\alert}[1]{\textbf{#1}}

\title{Climate Change Health Impact Assessments:  Farmer Suicide and Drought Case Study.}
\author{Ivan Hanigan$^1$, David Fisher$^2$, Steven McEachern$^3$}
\date{\today}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs Org-mode version 7.9.3f}}

@@

\begin{itemize}
\item General tools for Climate Change Health Impact Assessments (CCHIA)
\item Enhanced capacity for experimentation, reviews, revisions and re-iterations
\end{itemize}

Current approach:
\begin{itemize}
\item historical baseline exposure-response functions, control for some covariates
\item use response function with changed exposures and population at risk
\end{itemize}
\end{frame}
\section{Methods}
\label{sec-2}
\begin{frame}
\frametitle{Historical (Hanigan et al, 2012, \emph{PNAS}, 109)}
\label{sec-2-1}

\begin{footnotesize}
\begin{itemize}
\item {\color{red}Restricted Health and Drought data} and 
\item {\color{blue}Less Restricted Population data} 
\end{itemize}
(Colours refer to data storage and access rules shown in Figure 1).
\begin{eqnarray*}
        log({\color{red} O_{ijk}})  & = & s({\color{red}ExposureVariable})  + {\color{blue} OtherExplanators}  \\
        & &   + AgeGroup_{i} + Sex_{j} \\
        & &   + {\color{blue} SpatialZone_{k}}  \\
        & &  + sin(Time \times 2 \times \pi) + cos(Time \times 2 \times \pi) \\
        & &  + Trend \\
        & &   + offset({\color{blue} log(Pop_{ijk})})\\
\end{eqnarray*}
\end{footnotesize}
\begin{tiny}
\noindent Where:\\
        \indent ${\color{red}O_{ijk}}$ = Outcome (counts) by Age$_{i}$, Sex$_{j}$ and SpatialZone$_{k}$ \\
        \indent {\color{red}ExposureVariable} = Data with {\color{red}Restrictive Intellectual Property~(IP)} \\
        \indent {\color{blue}OtherExplanators} = Other {\color{blue}Less Restricted}  Explanatory variables \\
        \indent s( ) = penalized regression splines \\
        \indent ${\color{blue} SpatialZone_{k}}$  = {\color{blue} Less Restricted} data representing the $SpatialZone_{k}$  \\
        \indent Trend = Longterm smooth trend(s) \\
        \indent ${\color{blue}Pop_{ijk}}$ = interpolated Census populations, by time in each group\\
\end{tiny}
\end{frame}
\begin{frame}
\frametitle{Historical (Hanigan et al, 2012, \emph{PNAS}, 109)}
\label{sec-2-2}

\begin{itemize}
\item 38 years suicide rates with drought by 11 regions, age and sex
\item Estimated 9\% in rural males aged 30-49 due to drought over the period
\item Increased for rural males 10-29 y
\item Association with hot temp + spring
\end{itemize}
\end{frame}
\begin{frame}
\frametitle{Future (Bambrick et al, 2008, Garnaut Review)}
\label{sec-2-3}

@@

\end{footnotesize}
\end{frame}
\section{Results}
\label{sec-3}
\begin{frame}
\frametitle{Drought-suicide response function}
\label{sec-3-1}

\begin{figure}[!h]
\centering
\includegraphics[width=.5\textwidth]{Figure1.png}
\caption{Figure1.png}
\label{fig:Figure1.png}
\end{figure}
\end{frame}
\begin{frame}
\frametitle{Criticism}
\label{sec-3-2}

This model is too static, reductionist, reality is more complex. Need to work more on interactions with non-climate factors especially: 
\begin{itemize}
\item Natural capital
\item Financial capital
\item Social capital
\item Physical capital and
\item Human capital
\end{itemize}
\end{frame}
\section{Conclusion}
\label{sec-4}
\begin{frame}
\frametitle{Conclusion}
\label{sec-4-1}

\begin{itemize}
\item Drought is related to increased suicide risk in Australia
\item Future Drought associated deaths can be calculated
\item These estimates will be very uncertain, contentious and difficult to justify
\item New technology is needed to enable rigorous and transparent exploration
\end{itemize}
\end{frame}
\section{Acknowledgements}
\label{sec-5}
\begin{frame}
\frametitle{Acknowledgements}
\label{sec-5-1}

\includegraphics[width=4cm]{ANU_LOGO_cmyk_56mm.png}
\includegraphics[width=2cm]{andslogo.pdf}
\includegraphics[width=3cm]{deptlogo.pdf} \\
\begin{footnotesize}
This project is supported by the Australian National Data Service through the National Collaborative Research Infrastructure Strategy Program and the Education Investment Fund (EIF) Super Science Initiative.

More information from \texttt{ivan.hanigan@gmail.com} or at \texttt{[[http://opensoftware-restricteddata.github.io][http://opensoftware-restricteddata.github.io]]}

\end{footnotesize}
\end{frame}
\section{References}
\label{sec-6}
\begin{frame}
\frametitle{References}
\label{sec-6-1}
